Solutions for decentralized AI\\

### 2023-06-17 paper.tex
Paper 80% finished

\author{\IEEEauthorblockN{Sergi Hernández Burbano de Lara}
\IEEEauthorblockA{\textit{Data Science Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.hernandez01@estudiant.upf.edu}
\and
\IEEEauthorblockN{Sergi Vila Oriol}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.vila02@estudiant.upf.edu}
\and
\IEEEauthorblockN{Edgar Espinós Murria}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
edgar.espinos01@estudiant.upf.edu}
}
\maketitle

@@

    Except for Proof-of-Deep-Learning (2019), where they assumed a single supplier that should be honest, all the other suggested protocols require problem suppliers to provide a reward for the winning miner.

@@

    \subsection{Experiment in Python}

    We will implement our own Deep Learning consensus protocol in Python and simulate a network of nodes running this protocol where one of them is Byzantine and executes the attack discussed above: performing the submitter and miner roles simultaneously and submitting pre-solved problems to the pool in order to gain the newly-minted rewards with higher probability than the honest nodes.

@@

    Having seen that it is impossible to have such a deep learning setting implemented in the consensus protocol of the Blockchain, we ask ourselves if it would be feasible to have it implemented in smart contracts.

@@

    \subsection{Experiment in Solidity and Brownie}
    We wanted to test how expensive it would be to train a simple model like a linear regression model in a smart contract.

>>>>

\author{\IEEEauthorblockN{Sergi Hernández Burbano de Lara}
\IEEEauthorblockA{\textit{Data Science Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.hernandez01@estudiant.upf.edu}
\and
\IEEEauthorblockN{Sergi Vila Oriol}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
sergi.vila01@estudiant.upf.edu}
\and
\IEEEauthorblockN{Edgar Espinós Murria}
\IEEEauthorblockA{\textit{Telecoms Engineering Student} \\
\textit{Universitat Pompeu Fabra}\\
Barcelona, Spain \\
edgar.espinos01@estudiant.upf.edu}
}
\maketitle

@@

Except for Proof-of-Deep-Learning (2019), where they assumed a single supplier that should be honest, all the other suggested protocols require problem suppliers to provide a reward for the winning miner. The authors of CrowdMine even propose burning part of the rewards instead of giving it in full to the winner.

@@

\subsection{Protocol sketch}

We have implemented our own functional Deep Learning consensus protocol so that in the next section we are able to do simulations in Python.

The protocol we implemented was based on some ideas from previously published protocols and other ideas of our own. It is designed to be easy to implement and simple to understand. Its correctness and safety are still to be studied.

It has two possible entities:

\begin{itemize}
\item ``submitters'' that wish to outsource the work of discovering a model $f$ that maps some input distribution $X$ to an output distribution $Y$ with the maximum accuracy possible;
\item and ``miners'' that are willing to find that model $f$, which depends on parameters $W$ and other hyperparameters.
\end{itemize} 
Miners try to solve the same problem all at the same time. We assume there is a method for all the miners to agree on the order of the submitters (it could be in a FIFO order, or by the amount of rewards they provide if any).

The protocol runs for sequential rounds at the end of which all honest nodes should agree on one block to be appended to their local histories. Each round has three phases:
\begin{enumerate}
    \item ``Training phase'', in which:
    \begin{enumerate}
        \item the submitter broadcasts a training dataset $\{\mathcal X_\text{train},\mathcal Y_\text{train}\}$ to all miners;
        \item miners train their models $\{f,W\}$ using the training data;
        \item miners have to commit to their final model $\{f,W\}$ by sending a hash of it to the submitter before a timeout.
    \end{enumerate}
    \item ``Evaluation phase'', in which:
    \begin{enumerate}
        \item the submitter broadcasts the test input $\mathcal X_\text{test}$ to all miners;
        \item miners compute their estimates for the test output using their model $f(x_{test}|W)=\hat y_{test}$;
        \item miners send their estimates $\hat{\mathcal Y}_{\text{test}}$ to the submitter;
        \item the submitter computes the accuracy of the model of each miner by comparing their estimates $\hat{\mathcal Y}_{\text{test}}$ with the real test dataset $\mathcal Y_{\text{test}}$.
    \end{enumerate}
    \item ``Awarding phase'', in which:
    \begin{enumerate}
        \item the submitter ranks miners by their accuracy;
        \item the submitter sends a signed message to the miner with most accuracy certifying it as the winner of the round;
        \item the submitter sends the hash of the model and the estimate $\hat{\mathcal Y}_{\text{test}}$ of the winner to all the miners;
        \item the winner is then allowed to build a block in which he will have to include the signed certificate of the submitter and the model $\{f,W\}$;
        \item the block is broadcasted to all other miners;
        \item miners verify the block by checking that:
        \begin{enumerate}
            \item it includes the certificate of the submitter of the round,
            \item the hash of the published model $\{f,W\}$ corresponds with the hash the winner committed to during the training phase,
            \item and that the published model $\{f,W\}$ indeed maps $\mathcal X_\text{test}$ to the estimate $\hat{\mathcal Y}_{\text{test}}$ to which the winner committed to during the evaluation phase.
        \end{enumerate}
        If the published model does not correspond with the hash or is not the model that the winner used to compute $\hat{\mathcal Y}_{\text{test}}$, honest nodes won't add the block to their histories and will notify the misconduct to the submitter that will choose the next model with best accuracy and will start again from step 3b.

        If the model is correctly published, honest nodes add the block to their local history and a new round starts.
    \end{enumerate}
\end{enumerate}

This protocol certainly works assuming honest behavior from all players and is designed to be resistant to some attacks. Nonetheless, by now, it is just designed for testing purposes.

With the definition above, the protocol does not force submitters to pay a fee or provide a reward. By now, we will assume it is not necessary and test the assumption in the experiment in the following section.

\subsection{Experiment in Python}
After implementing the aforementioned protocol, we simulate a network of nodes running the protocol where one of them is Byzantine and executes the attack discussed before: performing the submitter and miner roles simultaneously and submitting pre-solved problems to the pool in order to gain the newly-minted rewards with higher probability than the honest nodes.

So, from the proof sketch and the experiment, we conclude that without rewards and/or fees provided by the submitters, miners can manipulate their probability of mining a block and thus win the reward.

@@

Having seen that it is impossible to have such a decentralized AI solution implemented in the consensus protocol of the Blockchain, we ask ourselves if it would be feasible to have it implemented in smart contracts.

@@

\subsection{Experiment in Solidity and Brownie}

We wanted to test how expensive it would be to train a simple model like a linear regression model in a smart contract.
